Response to the defense feedback

### 2021-06-16 Chapter-4/Chapter-4.tex
Updates from Overleaf

\subsubsection*{Password Checker}
\begin{figure}
  \begin{minipage}{0.8\linewidth}
    \begin{lstlisting}[xleftmargin=.2\textwidth, xrightmargin=.0\textwidth, frame=none]
bool pwcheck(uint8_t *key, uint8_t *pub) {
  for (int i = 0; i < 2; ++i) {
    if (key[i] != pub[i]) {
      return false;
    }
  }
  return true;
}
\end{lstlisting}\caption{A vulnerable password checker.}\label{fig:chapter4:pwcheck1}
  \end{minipage}
  \vfill
  \begin{minipage}{0.8\linewidth}
    \begin{lstlisting}[xleftmargin=.2\textwidth, xrightmargin=.00\textwidth, frame=none]
bool pwcheck(uint8_t *key, uint8_t *pub) {
  bool matched = true;
  for (int i = 0; i < 2; ++i) {
    if (pub[i] != key[i]) 
      matched = false;
  }
  return matched;
}
\end{lstlisting}\caption{A safe password checker.}\label{fig:chapter4:pwcheck2}
\end{minipage}
\end{figure}

>>>>

\subsubsection*{Password Checker}

\begin{figure}
  \begin{minipage}{0.8\linewidth}
    \begin{lstlisting}[xleftmargin=.2\textwidth, xrightmargin=.0\textwidth, frame=none]
bool pwcheck(uint8_t *key, uint8_t *pub) {
  for (int i = 0; i < 2; ++i) {
    if (key[i] != pub[i]) {
      return false;
    }
  }
  return true;
}
\end{lstlisting}\caption{A vulnerable password checker.}\label{fig:chapter4:pwcheck1}
  \end{minipage}

  \vfill

  \begin{minipage}{0.8\linewidth}
    \begin{lstlisting}[xleftmargin=.2\textwidth, xrightmargin=.00\textwidth, frame=none]

bool pwcheck(uint8_t *key, uint8_t *pub) {
  bool matched = true;
  for (int i = 0; i < 2; ++i) {
    if (pub[i] != key[i]) 
      matched = false;
  }
  return matched;
}
\end{lstlisting}\caption{A safe password checker.}\label{fig:chapter4:pwcheck2}
\end{minipage}
\end{figure}
